\documentclass{article}


\usepackage{indentfirst}
\usepackage[utf8]{inputenc}
\usepackage{titlesec}
%\titlespacing*{\section} {0pt}{3.5ex plus 1ex minus .2ex}{1ex plus .2ex}
%\titlespacing*{\subsection} {0pt}{1.5ex plus 0ex minus 2ex}{-2ex plus .25ex}
%\titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\usepackage{fancyhdr}
\usepackage{xcolor}
\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{rem}[thm]{Remark}
\newtheorem{remark}[thm]{Remark}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{proof}[thm]{Proof}
\pagestyle{fancy}
\fancyhf{}
\rhead{Use cases}
\lhead{Project 23}
\rfoot{\thepage}

\usepackage{tocloft}
\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}
\renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}

\usepackage[]{algorithm2e}
\usepackage{enumitem}
\usepackage{pgfplots}
\usepackage{float}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{rotating}
\usetikzlibrary{automata, positioning, arrows}
\pgfplotsset{compat=1.10}
\usepgfplotslibrary{fillbetween}

\begin{document}

\section*{Regular user login}
\subsection*{Id: login\_reg\_user}
\noindent
\textbf{Remarks:}\\
 The \underline{underlined} text presents actions which happen outside the application. \\
 The \textbf{bold} text represents pparts which reveal the internal working of the app and that are not visible to the users / admins.
\begin{enumerate}
	\item \underline{The user gets invited by an admin. The admin registers the user with some data which he collects}
	\item \textbf{The app registers the user. It does not jet generate the secret token}
	\item The admin gets feedback about the successful registration
	\item \underline{The user joins the conference}
	\item The admin uses a function to display the user data
	\item \underline{The user is prompted to check his data, as only admins can edit it}
	\item \underline{The user tells the admin that there is a typo somewhere}
	\item The admin uses a function to edit the incorrect data.
	\item The admin uses a function to generate a password. \textbf{The app generates a secret token and a password and stores them. It also stores that the password is unused and that the user is currently loged in on 0 devices}
	\item \underline{The user gets the password (either as text or an qr code) from the admin. The user uses it to login} 
	\item \textbf{The app checks the password, send out the token, marks the password as used in order to prevent multiple logins and increments the device count of the user}
	\item \underline{The user decides to log in on a second device}
	\item The user presses a button in order to receive a new password
	\item \textbf{The app generates a new password and sends it to the user}
	\item The password gets displayed on the first device and can be used to log in on the second device
	\item \textbf{Step 6 gets repeated. The same token gets sent}
\end{enumerate}

\end{document}