\documentclass{article}


\usepackage{indentfirst}
\usepackage[utf8]{inputenc}
\usepackage{titlesec}
%\titlespacing*{\section} {0pt}{3.5ex plus 1ex minus .2ex}{1ex plus .2ex}
%\titlespacing*{\subsection} {0pt}{1.5ex plus 0ex minus 2ex}{-2ex plus .25ex}
%\titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\usepackage{fancyhdr}
\usepackage{xcolor}
\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{rem}[thm]{Remark}
\newtheorem{remark}[thm]{Remark}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{proof}[thm]{Proof}
\pagestyle{fancy}
\fancyhf{}
\rhead{Use cases}
\lhead{Project 23}
\rfoot{\thepage}

\usepackage{tocloft}
\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}
\renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}

\usepackage[]{algorithm2e}
\usepackage{enumitem}
\usepackage{pgfplots}
\usepackage{float}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{rotating}
\usetikzlibrary{automata, positioning, arrows}
\pgfplotsset{compat=1.10}
\usepgfplotslibrary{fillbetween}

\begin{document}

\section*{Login failure - password in use}
\subsection*{Id: login\_failure\_1}
\noindent
\textbf{Remarks:}\\
 The \underline{underlined} text presents actions which happen outside the application. \\
 The \textbf{bold} text represents parts which reveal the internal working of the app and that are not visible to the users / admins.
\begin{enumerate}
	\item \underline{The user registers for a conference and recieves a password as usual}
	\item The user tries to log in.
	\item \textbf{The app notices that the password has already been used}
	\item The admins get feedback telling the user that there were multiple login attempts with the same password for the same user name. By default the account gets blocked.
	\item The app automatically protocols every attempt of double password usage.
	\item The user gets notified to visit a service desk immediately \footnote{It is best if the client (Timo) provides the exact text the user should see }
	\item \underline{The user goes to the service desk}
	\item If the user says that he accidentally used the password twice, then the admin can just unblock the account.
	\item If the user says that he never used the password before the admin can delete the data and re-register the user (There should be a button that allows for automatic re-registration, which leaves everything except the login data unchanged).

\end{enumerate}

\end{document}
