\documentclass{article}


\usepackage{indentfirst}
\usepackage[utf8]{inputenc}
\usepackage{titlesec}
%\titlespacing*{\section} {0pt}{3.5ex plus 1ex minus .2ex}{1ex plus .2ex}
%\titlespacing*{\subsection} {0pt}{1.5ex plus 0ex minus 2ex}{-2ex plus .25ex}
%\titlespacing*{\subsubsection}{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\usepackage{fancyhdr}
\usepackage{xcolor}
\newtheorem{thm}{Theorem}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{rem}[thm]{Remark}
\newtheorem{remark}[thm]{Remark}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{proof}[thm]{Proof}
\pagestyle{fancy}
\fancyhf{}
\rhead{Use cases}
\lhead{Project 23}
\rfoot{\thepage}

\usepackage{tocloft}
\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}
\renewcommand\cftsecleader{\cftdotfill{\cftdotsep}}

\usepackage[]{algorithm2e}
\usepackage{enumitem}
\usepackage{pgfplots}
\usepackage{float}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{rotating}
\usetikzlibrary{automata, positioning, arrows}
\pgfplotsset{compat=1.10}
\usepgfplotslibrary{fillbetween}

\begin{document}

\section*{Voting - Multiple vote submission}
\subsection*{Id: voting\_mult\_votes}
\noindent
\textbf{Remarks:}\\
 The \underline{underlined} text presents actions which happen outside the application. \\
 The \textbf{bold} text represents parts which reveal the internal working of the app and that are not visible to the users / admins.
\begin{enumerate}
	\item The admin starts a vote.
	\item The backend notices that there are two incoming votes from the same user.
	\item These votes are classified as malicious, since the attendees interface doesent allow multiple votes for the same vote. The system drops both votes and notifies the admins (but not the users). The admins do see who sent multiple votes but do not see what the user voted for. 
	\item The admins can chose how to react to this (ex. redo the vote, block the account of that user etc.)
\end{enumerate}

\end{document}
